---
title: "Methods 4 -- Portfolio Assignment 2"
output: html_notebook
editor_options: 
  chunk_output_type: inline
  markdown: 
    wrap: 72
---

-   *Type:* Group assignment
-   *Due:* 3 April 2022, 23:59

Hello CogSci's :)

In this portfolio, you are asked to do four tasks:

\- Make a DAG for something

\- Simulate data that fits the DAG

\- Use linear models to confirm that the DAG fits the data

\- Mess it up.

Each of the four tasks have some sub-steps.\
Report briefly what you find, for example in a markdown document, for
example called report.md so that the poor TA can easily get an overview
before looking in your code :)

Then you can also make a (brief!) explanation of the phenomenon you are
DAGGIN, simulating and modelling.

Looking forward !

## Task 1: The DAG

\- **Come up with an** incredibly interesting and scientifically
important made-up **example** for a phenomenon to investigate. Decide on
two variables (an outcome and a predictor) that you would like to
investigate the relation between. If in doubt, you **can be inspired by
Peter's amazing example** on the next page.

*In our example, we wish to investigate the effect of the predictor corona fear (CF) on*
*the outcome variable Infected (a binary variable taking either the value 0 or 1)*

*Since Denmark reported it's first case of COVID-19 contraction on the 27th February 2020 (STPS, 2020),* 
*COVID-19 and its development has been subject to extensive coverage in Danish media.*
*News media has a critical role in times of epidemic crises since*
*exposure to as well as consumption of information in times of pandemics*
*may alter people’s perception and provoke behavioural changes that*
*might ultimately impact the evolution and further spread of the virus (Gozzi et al., 2020).* 

*We therefore expect that corona fear is a sensible predictor of whether one*
*gets infected or not, assuming that the degree to which one fears*
*COVID determines the precautions and actions one take to avoid getting infected.* 

*Predictor: corona fear (continuous variable)* 
*Outcome variable: infection (0/1)*
*Sanitising: continuous variable* 
*FM variable: do you wear face mask according to the national guidelines? (for the sake of simplicity, we assume that this is a binary variable taking either the value 0 or 1, meaning that you either always where a face mark when the guidelines advises you to do that (1) and never wear it in situations were the national guidelines advises it. We do acknowledge that is a false dichotomy)*
*Germ level: the level of vira germs in your body. We have no biological evidence for a variable of this type, but for the sake of simplicity we assumes that the level of germs present in your body can be describes as a normally distributed continuous variable*

\- **Make a DAG** for the phenomenon. Make it medium complicated: that
means, make sure there are some different kinds of relations (see next
step). Change it if you don't get anything interesting for the next
steps.\
**Draw it** somehow (on paper, in R, laser engraved in diamond).\
**Code it** in dagitty (this is a nice tool:
<http://dagitty.net/dags.html> )

```{r}
pacman::p_load(usethis,dplyr, tidyverse, ggplot2, rstan, dagitty,ggdag)
library(rethinking)

#DAG corona
dag_corona<- dagitty( "dag {
    corona_fear -> sanitizing;
    sanitizing-> germ_level;
    face_mask -> germ_level;
    corona_fear -> face_mask;
    germ_level -> infected
}")

coordinates(dag_corona) <- list( 
  x=c(corona_fear =0,face_mask =-1, sanitizing =0, germ_level=-1, infected= -1), 
  y=c(corona_fear =0,face_mask =0, sanitizing = 1, germ_level=1, infected=2) )

drawdag(dag_corona)
```

```{r}
library(ggdag)

pretty_dag <- dagify(INF ~ GL,
      GL ~ FM + S,
      FM ~ CF,
      S ~ CF,
      labels = c("INF" = "Infected",
                 "FM" = "Face Mask",
                 "GL" = "Germ Level",
                 "CF" = "Corona Fear",
                 "S" = "Sanitising"),
      latent = c("FM","GL","S"), # latent variable = hidden variable
      exposure = "CF",
      outcome = "INF")

ggdag(pretty_dag, text = FALSE, use_labels = "label", stylized=FALSE)+remove_grid()+remove_axes()

```

```{r}
ggdag_paths(pretty_dag, text = FALSE, use_labels = "label", shadow = TRUE)
```

```{r}
ggdag_adjustment_set(pretty_dag, text = FALSE, use_labels = "label", shadow = TRUE)
```

\- Find **elemental forms of variable relations** in the DAG (i.e.,
forks, pipes, colliders, and their descendants).

Pipe

(FM -\> GERM -\> INFECTED)

(Cf --\> FM --\> GERM)

(CF -\> S -\> GERM)

(S --\> GERM --\> INFECTED)

Fork

(S \<- CF -\> FM)

Collider

(S -\> GERM \<- FM)


*We inspect the variable FM to depend on your corona fear, as we assume that a person who is really scared of COVID would be much more *
*likely to strictly follow the national guidelines, whereas a person who didn't fear corona at all would reversely be much less likely to*
*wear a face mask although the national guidelines advises one to do it* 

*The same goes for the relation between corona fear and sanitising. We expect a person with a high corona fear to have a much higher*
*daily frequency of sanitising than a person with no corona fear at all*.

*We would expect germ level to depend on whether you wear face mask when advised to or not, as* 
*the face mask (at least partly) prevents germs from entering your mouth and nose*.

*The same goes for the relation between germ level and sanitising, as*
*sanitising works by killing most germs, preventing them from entering your body*

*Lastly, we expect the level of germs to determine whether you are infected or not. With a low level of germs,*
*one would expect your immune system would be strong enough to fight the few germs that have entered your body.*
*However, if the level of germs in your body is extremely high, it might exceed the capacity of your immune system*
*to fight back, resulting in you getting infected.*


\- Find out **what variables to include (and not include)** in a
multiple linear regression to avoid 'back door' (AKA non-causal) paths.
Do this first with your eyes and your mind. Then you can use dagitty's
function `adjustmentSets()`.

```{r}
# Shutting the backdoor - analyzing the graph to block the backdoor
adjustmentSets(dag_corona,exposure="corona_fear", outcome="infected")
```

*OBS: nothing here = No backdoors to shut (no confounding paths between
Corona Fear and Infected)*

Chris: our input is CF (predictor, our intervention), our outcome is
(infected). We don't have any backdoor paths, all paths are causal. If
FM was a collider, it would be a common cause/confound that we would
have to account for (hold constant) to close the backdown. We could aadd
something that affects both FM and Germ_lvl. To have the total causal
effect, we only need CF and Inf in out model (if we include FM and S,
the coefficient for CF would just return the prior. Tge estimate for
htis coefficient would be its own prior).

*You can ask your computer to reproduce this analysis, to analyze the
graph and find the necessary variables to control for in order to block
the backdoor. The dagitty R package provides adjustmentSets for this
purpose*

In order to shut the backdoor. Here's the recipe: (1) List all of the
paths connecting X (the potential cause of interest) and Y (the out-
come). (2) Classify each path by whether it is open or closed. A path is
open unless it contains a collider. (3) Classify each path by whether it
is a backdoor path. A backdoor path has an arrow entering X. (4) If
there are any backdoor paths that are also open, decide which
variable(s) to con- dition on to close it. Let's consider some examples.

\- Find out which **conditional independencies** the DAG implies. First
with the mind, then with daggity's function
`impliedConditionalIndependencies()`.

First, we find out which conditional independencies the DAG implies.

Pipe

(FM -\> GERM -\> INFECTED)

(Cf --\> FM --\> GERM)

(CF -\> S -\> GERM)

(S --\> GERM --\> INFECTED)

Fork

(S \<- CF -\> FM)

Collider

(S -\> GERM \<- FM)

```{r}
# Deriving our DAG’s conditional independencies
impliedConditionalIndependencies(dag_corona)
```
   
   
    crn_ _||_ grm_ | fc_m, sntz
    
    crn_ _||_ infc_ | grm_
    *If we stratify by G, there is no association between CF and Infection*

    crn_ _||_ infc_ | fc_m, sntz
    *OBS*

    fc_m _||_ infc_ | grm_
    *OBS*

    fc_m _||_ sntz | crn_
    *OBS*

    infc_ _||_ sntz | grm_
    *OBS*


OBS: WE NEED TO EXPLAIN HERE. Chris said the following in the lecture of
week 5: "there are a lot of implications of a DAG. There are different
ways to test its implication. Use \*dagitty\* to get a list of testable
implications (and go through this list one by one. If one of them is not
fulfilled, you can falsify your DAG - but you can't prove; you can only
say \*"This DAG is compatible with the data - there may be other
DAGs"\*.

########################################################################################## 

########################################################################################## 

p(FM)= S(CF)

CF is a continuum: as the fear increases, the probability of putting on
mask increases. HOW do we simulate it? We can sim fear as normally
distributed(0,1) which would give us a Gaussian. Then u say that whether
a person puts on mask or not (FM) is rbern (1, sCP)).

P(FM) = 1/1+exp(CP). That you use!!!

s(P

Sigmoid transformation (from min if to if), but prob can only be from 0
to 1.

sCF (sigmoid transformation )

GL \~ rnorm(mu, sigma)

mu = b0+b1x1+b2x2

continuous --\> bernomial (you translate to probability)

########################################################################################## 

########################################################################################## 

\- Find the full list of **Markov equivalent** DAGS. Use daggity's
function `equivalentGraphs()`.

The equivalentGraphs() function outputs a set of DAGs with the same
conditional independencies is known as a Markov equivalence set.

The list outputted allow show us 3 DAGS that would have the exact same
conditional independencies as our dag_corona has.

```{r}
equivalentDAGs(dag_corona)
```

Chris: We will get back the prior if we try to predict one thing from
the other

## Task 2: The data

\- **Simulate some data that fits the DAG.** There are many ways to do
this. A simple way is just to sample one variable from a normal
distribution which has another variable as mean. McElreath does this in
the book a few times, and you can use this as inspiration.

*Corona Fear* Normal

*Face Mask* Binomial

*Sanitizing* Poisson

*Germ Level* Normal

*Infected* Binomial

```{r}
set.seed(1)
N= 10000

# Simulating variables:

# OCD
OCD_w <- sample(1:5, size=N, replace=TRUE, prob=c(.8, .10, .05, .03, .02))

# Corona fear (assuming that it is normally distributed)
corona_fear <-rnorm(N, mean=50+(0.05*OCD_w), sd=10) 

# Face mask (is dependent on corona_fear)
face_mask <- rbinom(N, size =1, prob=inv_logit(scale(corona_fear)))
plot(corona_fear, inv_logit(scale(corona_fear)), main= "Sigmoid plot: probability of wearing a face mask given corona fear")

# Sanitizing (is dependent on corona_feat)
sanitizing <-  rnorm(N, mean= (corona_fear-20)+(OCD_w*1.2), sd=2) # OCD


# Germ level (is dependent on both sanitizing & whether you wear face mask or not)
germ_level <-  rnorm(N, mean= 5000 - ((sanitizing*10)*(1+face_mask)), sd=100)

# Probability of being infected (depends on your germ level)
infected <-  rbinom(N, size= 1, prob= inv_logit(scale(germ_level)))
plot(germ_level, inv_logit(scale(germ_level)), main= "Sigmoid plot: probability of being infected given germ level")

# creating df
df <- tibble(germ_level, sanitizing, infected, face_mask, corona_fear) 
```

*Standardizing variables*
Standardizing variables: OBS CHRIS: SHOULD WE STANDARDIZE A DICHOTOMOUS VARIABLE, FM? 
```{r}

df <- df %>% 
  mutate(germ_std=scale(germ_level),sanitizing_std= scale(sanitizing),  infected_std=scale(infected),face_mask_std=scale(face_mask), corona_fear_std= scale(corona_fear))

#ls.str(df)
```

## Task 3: Statistics
\- Run **multiple linear regression**s to **test the conditional
independencies** **implied by your DAG**. Make sure to avoid backdoor
paths. See that the linear model shows the conditional independencies
implied by your DAG, implying that the data and the DAG are compatible
(if the linear model doesn't show the conditional independencies implied
by the DAG, the data and the DAG doesn't fit).

### Testing the conditional independencies
Model 1: crn_ _||_ grm_ | fc_m, sntz. 
Testing whether the causal coefficient germ_level is insignificant when stratifying by face_mask and sanitizing. 
```{r}
m1<- quap(
    alist(
        corona_fear_std ~ dnorm( mu , sigma ) ,
        mu <- a  + bGermLevel*germ_std + bFaceMask*face_mask_std + bSanitizing*sanitizing_std,
        a ~ dnorm( 0 , 0.2 ) ,
        bGermLevel~ dnorm( 0 , 1 ),
        bFaceMask~ dnorm( 0 , 1 ) ,
        bSanitizing ~ dnorm( 0 , 1 ),
        sigma ~ dexp( 1 )
    ) , data = df )

plot(coeftab(m1),by.model=TRUE )
```
As seen in the above plot, corona fear and germ level becomes independent (i.e., the model with almost no uncertainty estimates the coefficient bGermLevel to be very close to zero ) when stratifying by face_mask and sanitizing. 


Model 2: crn_ _||_ infc | grm_
Testing whether the causal coefficient infc (being infected or not) is insignificant when stratifying by germ_level. 
```{r}

m2<- quap(
    alist(
        corona_fear_std ~ dnorm( mu , sigma ) ,
        mu <- a + bInfected*infected_std  + bGermLevel*germ_std,
        a ~ dnorm( 0 , 0.2 ) ,
        bInfected ~ dnorm( 0 , 1 ) ,
        bGermLevel~ dnorm( 0 , 1 ),
        sigma ~ dexp( 1 )
    ) , data = df )

plot(coeftab(m2), par=c("bInfected", "bGermLevel" ))

```
As seen in the above plot, corona fear and infected becomes independent (i.e., the model confidently estimates the coefficient bInfected to be very close to zero) when stratifying by germ_level. 


Model 3: crn_ _||_ infc_ | fc_m, sntz
Testing whether the causal coefficient bInfected is insignificant when stratifying by face_mask and sanitizing. 
```{r}

m3 <- quap(
    alist(
        corona_fear_std ~ dnorm( mu , sigma ) ,
        mu <- a + bInfected * infected_std  + bFaceMask * face_mask_std + bSanitizing * sanitizing_std,
        a ~ dnorm( 0 , 0.2 ) ,
        bInfected ~ dnorm( 0 , 1 ),
        bFaceMask ~ dnorm( 0, 1 ),
        bSanitizing~ dnorm( 0 , 1 ),
        sigma ~ dexp( 1 ) # Contains no more info than an average deviation. The avg. is just the inverse of the rate, 1. 
    ) , data = df )


plot(coeftab(m3),by.model=TRUE )
```
As seen in the above plot, bInfected becomes independent (i.e., the model does with almost no uncertainty estimate the coefficient bInfected to be very close to zero) when stratifying by face_mask and sanitizing. 


Model 4: fc_m _||_ infc_ | grm_
Testing whether the causal coefficient infc (being infected or not) significantly close to zero when stratifying by germ_level in a model that has face_mask as outcome variable.
```{R} 

m4 <- quap(
    alist(
        face_mask_std ~ dnorm( mu , sigma ) ,
        mu <- a + bInfected*infected_std  + bGermLevel*germ_std,
        a ~ dnorm( 0 , 0.2 ) ,
        bInfected ~ dnorm( 0 , 1 ) ,
        bGermLevel~ dnorm( 0 , 1 ),
        sigma ~ dexp( 1 )
    ) , data = df )

plot(coeftab(m4),by.model=TRUE)

```
As seen in the above plot, bGermLevel becomes independent (i.e., the model does with almost no uncertainty estimate the coefficient bInfected to be very close to zero) when stratifying by germ level.

Model 5: fc_m _||_ sntz | crn_
Testing whether the causal coefficient of sanitizing becomes significantly close to zero when stratifying by corona fear in a model that has face_mask as outcome variable.
```{R} 

m5 <- quap(
    alist(
        face_mask ~ dnorm( mu , sigma ) ,
        mu <- a + bSanitizing*sanitizing_std  + bCoronaFear*corona_fear_std,
        a ~ dnorm( 0 , 0.2 ) ,
        bSanitizing ~ dnorm( 0 , 1 ) ,
        bCoronaFear~ dnorm( 0 , 1 ),
        sigma ~ dexp( 1 )
    ) , data = df )

plot(coeftab(m5),by.model=TRUE)
```
The coefficient bSanitizing is still close to zero, but not as confidently estimated as zero as in the previous plots. OBS CHRIS: can we say that the coefficient bSanitizing is close to zero (thus in accordance with our dag), or does such as small deviation from 0 count as a violation of the implications of our DAG???? 

Model 6: infc_ _||_ sntz | grm_
Testing whether the causal coefficient of sanitizing becomes significantly close to zero when stratifying by germ level in a model that has infected as outcome variable.
```{R} 

m6 <- quap(
    alist(
        infected_std ~ dnorm( mu , sigma ) ,
        mu <- a + bSanitizing*sanitizing_std  + bGermLevel*germ_std,
        a ~ dnorm(0,0.2) ,
        bSanitizing ~ dnorm(0,1) ,
        bGermLevel~ dnorm(0,1),
        sigma ~ dexp(1)
    ) , data = df )

plot(coeftab(m6),by.model=TRUE)

```
As seen in the above plot, bSanitizing becomes independent from infection (i.e., the model does with almost no uncertainty estimate the coefficient bInfected to be very close to zero) when stratifying by germ level.



## Task 4: Messing it up

\- Try and **deliberately have an open back door path** and see if you can get wrong inference.

We now create a DAG that has the variable OCD as backdoor that directly influences both corona fear and sanitizing. We expect a person with severe OCD sanitize more often (independently of corona fear), but also to fear corona more, which then has a direct influence on sanitizing as well. 

```{r}

# Twisted DAG corona
twisted_dag_corona <- dagitty( "dag {
    corona_fear -> sanitizing
    sanitizing-> germ_level
    OCD -> sanitizing
    OCD -> corona_fear
    face_mask -> germ_level
    corona_fear -> face_mask
    germ_level -> infected
}")

# Plotting the DAG
coordinates(twisted_dag_corona) <- list( 
  x=c(corona_fear =0, OCD = .3, face_mask =-.5, sanitizing =0, germ_level=-.5, infected= -.5) , 
  y=c(corona_fear =0, OCD = .5, face_mask =0, sanitizing = 1, germ_level=1, infected=2) )

drawdag(twisted_dag_corona)

# Shutting the backdoor - analyzing the graph to block the backdoor
adjustmentSets(twisted_dag_corona, exposure="corona_fear", outcome="infected")
```
Including OCD introduces an open backdoor path to infected. OCD is a confounded variable that may result in our model making wrong inferences.
When introducing OCD in the DAG, OCD creates a confounding path going from OCD --> SAN --> GL --> INF. We want to block it in order to avoid any spurious correlation that prevents us from seeing the actual effect that corona_fear has on infection. 

The path CF <- OCD -> sanitizing is a backdoor path because it enters corona fear with an arrow and also connects corona fear to sanitizing. This path is confounding.We can deconfound this model by stratifying by OCD. Since sanitizing and corona fear in the above dag share the common cause, OCD, we can separate them statistically by stratifying by their common cause, OCD.

OBS: JØRGEN. In this case, controlling for OCD ruins inference as it does not belong to the causal path from corona fear to corona infected. Why? Because if only the 2 path (as descibed above) existed and we decided to change CF it wouldn't affect INF. To account for this, we could isolate OCD (the confounder) by adding it to the model by conditioning on it. When conditioning, we're analyzing the values of the other variables for a given value of the conditioned variable. This would block the second path and thus allow for inclusion of OCD in the model. 

\- Try and deliberately **simulate some data that doesn't fit the DAG**,
or **create a new DAG that doesn't fit the data**.
```{r}

# Corona fear (assuming that it is normally distributed)
corona_fear_w <-rnorm(N, mean=50, sd=10)

# Face mask (depending on germ level)
face_mask_w <- rbinom(N, size =1, prob= inv_logit(scale(germ_level)))

# Sanitizing (depending on germ_level)
sanitizing_w <- rnorm(N, mean= germ_level-20, sd=2)

# Germ level (depending on corona fear and face mask)
germ_level_w <-  rnorm(N, mean= 5000 - ((corona_fear*10)*(1+face_mask)), sd=100)

# Infected (not depending on any of the variables)
infected_w <-  rbinom(N, size= 1, prob=0.2)


# OCD level
OCD_w <- sample(1:5, size=N, replace=TRUE, prob=c(.8, .10, .05, .03, .02)) # 80% of not having OCD, apx. 2% chance for severe OCD

# creating df
df_w <- tibble(germ_level_w, sanitizing_w, infected_w, face_mask_w, corona_fear_w, OCD_w) 



```

### Standardizing variables: OBS CHRIS: SHOULD WE STANDARDIZE A DICHOTOMOUS VARIABLE, FM? 
```{r}

df_w <- df_w %>% 
  mutate(germ_std_w=scale(germ_level_w),sanitizing_std_w= scale(sanitizing_w),  infected_std_w=scale(infected_w),face_mask_std_w=scale(face_mask_w), corona_fear_std_w= scale(corona_fear_w), OCD_std_w = scale(OCD_w))

```

### Implied conditional independencies
```{r}

impliedConditionalIndependencies(twisted_dag_corona)

```

OCD _||_ fc_m | crn_
OCD _||_ grm_ | fc_m, sntz
OCD _||_ grm_ | crn_, sntz
OCD _||_ infc | grm_
OCD _||_ infc | fc_m, sntz
OCD _||_ infc | crn_, sntz

\- Use the same approach as above to **show that the DAG is wrong** (by
showing that conditional independencies don't exist in the data, for
example)

### Testing implied conditional independencies
```{r}
######### MODEL 1 wrong ################
# OCD _||_ fc_m | crn_
model1_w <- quap(
    alist(
        OCD_std_w ~ dnorm( mu , sigma ) ,
        mu <- a + bFaceMask*face_mask_std_w + bCoronaFear*corona_fear_std_w,
        a ~ dnorm( 0 , 0.2 ) ,
        bCoronaFear ~ dnorm( 0 , 0.5 ) ,
        bFaceMask ~ dnorm( 0 , 0.5 ) ,
        sigma ~ dexp( 1 ) # OBS : why exp? It doesn't change anything changing it to dnorm or dunif
    ) , data = df_w )

precis( model1_w )

plot(precis( model1_w ))

######### MODEL 2 wrong ################
# crn_ _||_ grm_ | fc_m, sntz
# OCD _||_ grm_ | fc_m, sntz
model2_w <- quap(
    alist(
        OCD_std_w ~ dnorm( mu , sigma ) ,
        mu <- a + bGermLevel*germ_std_w + bFaceMask*face_mask_std_w + bSanitize*sanitizing_std_w ,
        a ~ dnorm( 0 , 0.2 ) ,
        bGermLevel ~ dnorm( 0 , 0.5 ) ,
        bFaceMask ~ dnorm( 0 , 0.5 ) ,
        bSanitize ~ dunif( 0 , 0.5 ) ,
        sigma ~ dexp( 1 ) # OBS : why exp? It doesn't change anything changing it to dnorm or dunif
    ) , data = df_w )

precis( model2_w )

plot(precis( model2_w ))

#### MODEL 3
#OCD || grm_ | crn_, sntz
model3_w<- quap(
    alist(
        OCD_std_w ~ dnorm( mu , sigma ) ,
        mu <- a  + bGermLevel*germ_std_w + bCoronaFear*corona_fear_std_w+ bSanitizing*sanitizing_std_w,
        a ~ dnorm( 0 , 0.2 ) ,
        bGermLevel~ dnorm( 0 , 1 ) ,
        bCoronaFear~ dnorm( 0 , 1 ),
        bSanitizing ~ dnorm( 0 , 1 ),
        sigma ~ dexp( 1 )
    ) , data = df_w )
precis(model3_w)

plot(coeftab(model3_w),by.model=TRUE )

#### MODEL 4
#OCD || infc | grm_
model4_w<- quap(
    alist(
        OCD_std_w ~ dnorm( mu , sigma ) ,
        mu <- a  + bInfected*infected_std_w + bGermLevel*germ_std_w,
        a ~ dnorm( 0 , 0.2 ) ,
        bInfected ~ dnorm( 0 , 1 ),
        bGermLevel~ dnorm( 0 , 1 ) ,
        sigma ~ dexp( 1 )
    ) , data = df_w )

precis(model4_w)
plot(coeftab(model4_w),by.model=TRUE )


#### MODEL 5
# OCD _||_ infc | fc_m, sntz # 5

model5_w<- quap(
    alist(
        OCD_std_w ~ dnorm( mu , sigma ) ,
        mu <- a + bInfected*infected_std_w  + bFace_mask*face_mask_std_w + bSanitizing*sanitizing_std_w,
        a ~ dnorm( 0 , 0.2 ) ,
        bInfected~ dnorm( 0 , 1 ) ,
        bFace_mask~ dnorm( 0 , 1 ),
        bSanitizing~ dnorm( 0 , 1 ),
        sigma ~ dexp( 1 )
    ) , data = df_w )
precis( model5_w)

plot(precis(model5_w))

#### MODEL 6
# OCD _||_ infc | crn_, sntz # 6
model6_w<- quap(
    alist(
        OCD_std_w ~ dnorm( mu , sigma ) ,
        mu <- a + bInfected*infected_std_w  + bCorona_fear*corona_fear_std_w + bSanitizing*sanitizing_std_w,
        a ~ dnorm( 0 , 0.2 ) ,
        bInfected~ dnorm( 0 , 1 ) ,
        bCorona_fear~ dnorm( 0 , 1 ),
        bSanitizing~ dnorm( 0 , 1 ),
        sigma ~ dexp( 1 )
    ) , data = df_w )
precis( model6_w)

plot(precis(model6_w))
```



## Peter's perfectly optimal and extremely interesting example

*In a galaxy far, far away...*

*It is a period of civil wars in the galaxy. A brave alliance of
underground freedom fighters has challenged the tyranny and oppression
of the awesome GALACTIC EMPIRE.*

*To crush the rebellion once and for all, the EMPIRE is constructing a
sinister new battle station. Powerful enough to destroy an entire
planet, its completion spells certain doom for the champions of
freedom.*

*The evil Emperor has figured out, however, that neither the battle
station nor the Force can help him avoid that more solar systems join
the rebellion. He has therefore hired a CogSci student to use causal
modelling and multiple linear regressions to investigate how the
activity of the Death Star and other factors affects the probability
that a given solar system will join the rebellion (this allows him to
more optimally suppress freedom in the Galaxy).*

*You are that student.*

We assume that the probability of a solar system joining the rebellion
depends on\
- how many rebellion sympathizers there is in the system (more rebels
-\> higher probability of joining the rebellion)\
- how scared people are in the system (more scared -\> lower probability
of joining the rebellion).

How many rebellion sympathizers there is in a system depends on

\- crime levels (less crime -\> less rebellion sympathizers)

\- number of planets recently destroyed by the Death Star (more planets
destroyed -\> more rebellion sympathizers)

\- number of Jedis in the system (more Jedis -\> more rebellion
sympathizers)

How scared people are depends on

\- whether or not the Death Star is nearby (nearby -\> more scared)

\- how many jedis are in the system (more Jedis -\> less scared)

\- how much time Darth Vader has spent in the system recently (more time
-\> more scared)

Crime levels depend on

\- number of planets recently destroyed by the Death Star (more planets
destroyed -\> less crime)

And so on....




# References

STPS, S. F. P. (2020, February 27). Første dansker er bekræftet smittet med COVID-19 (ny
coronavirus)—Styrelsen for Patientsikkerhed. https://stps.dk/da/nyheder/2020/foerste-
dansker-er-bekraeftet-smittet-med-covid-19-ny-coronavirus/


Gozzi, N., Tizzani, M., Starnini, M., Ciulla, F., Paolotti, D., Panisson, A., & Perra, N. (2020). 
Collective Response to Media Coverage of the COVID-19 Pandemic on Reddit and Wikipedia: Mixed-Methods Analysis. Journal of Medical Internet Research, 22(10), e21597. https://doi.org/10.2196/21597


